In the preprocessing stage, the dataset must first be loaded into the program, the
required data parsed from the dataset, and any inconsistencies within the
dataset must be accounted for. Iconsistencies can include missing data, or any
redundant or unnecessary data.

\par The provided ``fake-news'' dataset is stored in the ``JSON'' format. This
hierarchical data type makes parsing relatively simple. The ``loadData.py''
file contains two methods, one for loading the data into a pandas DataFrame object,
and one for defining the target values and the features within the dataset.

\begin{lstlisting}[language=Python, caption={``loadJson'' function},
label={lst:loadJson}]
def loadJson(jsonFile, printMsgs=False):
	jsonInput = pd.read_json(jsonFile, lines=True)
	if(printMsgs == True):
		print(jsonInput.head())
		print("Shape:", jsonInput.shape)
		print("\nFeatures:", jsonInput.columns)
	return jsonInput
\end{lstlisting}

The function shown in Listing \ref{lst:loadJson} utilises the pandas python
library, and it's provided ``read\_json'' function. This function loads a json
file, with the given file path, to a pandas DataFrame object. As the provided
dataset contains each json object on a new line, the ``lines'' parameter of the
``read\_json'' function must be set to ``True'', telling the function to treat
each newline as a new json object.

\begin{lstlisting}[language=Python, caption={``splitFeaturesAndTargets''
function}, label={lst:splitFAndT}]
def splitFeaturesAndTargets(data, printMsgs=False):
	x = data[data.columns[1:]]
	y = data[data.columns[0]]
    	if(printMsgs == True):
		print("Feature Matrix:", x.head())
		print("\nResponse Vector", y.head())
	return x, y
\end{lstlisting}

The function shown in Listing \ref{lst:splitFAndT} performs the split of the
features from the dataset. The features chosen are the ``headlines'', and the
``article links''. The targets are chosen as the ``is\_sarcastic'' value, which is
the ground truth, i.e. indicates whether the headline is deemed to be sarcastic,
and therefore fall into the category of ``fake news''
